Expected Dependency Pair Match:\\ Predicting translation quality with expected syntactic structure

### 2009-05-15 mtjournal.tex
converted footnotes to endnotes.
still to do: endnotes must read sensibly out-of-context.

  \textbf{d\_50} and \textbf{d\_50\_var} measures.\footnote{Since

@@

To avoid this conflation, on the HTER corpora we report correlations
on $\bar{\mu}(m)$ and $\bar{\mu}(\textrm{HTER})$ (rather than measure
$m$ and HTER), where $\bar{\mu}$ represents mean-removal:
\begin{equation}
  \label{eq:meansub}
  \bar{\mu}(m(t_i)) = m(t_i) - \sum_{j=1}^I\frac{m(t_j)}{I}
\end{equation}
Mean-removal lowers the correlation $r$ values reported but ensures
that the reported correlations are among differences in the
translations rather than among differences in the underlying segments.
\footnote{ Previous work \cite{kahn08metricsmatr} reported HTER
  correlations against pairwise differences among translation segments
  derived from the same source segment. The results are similar to
  those reported here. However, we believe that pairwise differences
  introduce problems with the independence assumptions in the
  Pearson's $r$ tests, and we use mean-removal throughout this work
  instead.}

@@

% TO DO: more to say here?

@@

For these experiments, we use LDC Multiple Translation Chinese corpus
parts 2~\cite{LDC03MTC2} and 4~\cite{LDC06MTC4}.  These corpora
include multiple human judgments of fluency and adequacy for each
sentence, with each judgment using a different human judge and a
different reference translation.  For a rough\footnote{Our segment
  count differs from \inlinecite{owczarzak07labelleddepseval}, who
  report 16,800 segments over the same corpus. We find baseline
  correlations (BLEU$_4$ and TER) lower than those reported there as
  well, so the results presented here are not directly comparable with
  that paper, though we demonstrate similar gains over those baselines
  in essentially the same
  corpus. % (section~\ref{sec:facorr:newdeps}).}
} comparison with \inlinecite{owczarzak07labelleddepseval}, we treat
each judgment as a separate segment.
%
This treatment of this corpus yields 16,815 tuples of
$\langle$hypothesis, reference, fluency, adequacy$\rangle$.  In these
experiments, we extend this tuple with automatic scores derived from
$\langle$hypothesis, reference$\rangle$ and examine the
correlations\footnote{The independence of each of these segments is
  questionable, since the same hypothesis translations are used in
  multiple items, but for the sake of methodological comparison with
  prior work, this strategy is preserved.}  between those automatic
scores and the arithmetic mean of the fluency and adequacy measures.

@@

% \theendnotes

>>>>

  \textbf{d\_50} and \textbf{d\_50\_var} measures.\endnote{Since

@@

To avoid this conflation, on the HTER corpora we report correlations
on $\bar{\mu}(m)$ and $\bar{\mu}(\textrm{HTER})$ (rather than measure
$m$ and HTER), where $\bar{\mu}$ represents mean-removal:
\begin{equation}
  \label{eq:meansub}
  \bar{\mu}(m(t_i)) = m(t_i) - \sum_{j=1}^I\frac{m(t_j)}{I}
\end{equation}
Mean-removal lowers the correlation $r$ values reported but ensures
that the reported correlations are among differences in the
translations rather than among differences in the underlying segments.
\endnote{ Previous work \cite{kahn08metricsmatr} reported HTER
  correlations against pairwise differences among translation segments
  derived from the same source segment. The results are similar to
  those reported here. However, we believe that pairwise differences
  introduce problems with the independence assumptions in the
  Pearson's $r$ tests, and we use mean-removal throughout this work
  instead.}

@@

@@

For these experiments, we use LDC Multiple Translation Chinese corpus
parts 2~\cite{LDC03MTC2} and 4~\cite{LDC06MTC4}.  These corpora
include multiple human judgments of fluency and adequacy for each
sentence, with each judgment using a different human judge and a
different reference translation.  For a rough\endnote{Our segment
  count differs from \inlinecite{owczarzak07labelleddepseval}, who
  report 16,800 segments over the same corpus. We find baseline
  correlations (BLEU$_4$ and TER) lower than those reported there as
  well, so the results presented here are not directly comparable with
  that paper, though we demonstrate similar gains over those baselines
  in essentially the same
  corpus. % (section~\ref{sec:facorr:newdeps}).}
} comparison with \inlinecite{owczarzak07labelleddepseval}, we treat
each judgment as a separate segment.
%
This treatment of this corpus yields 16,815 tuples of
$\langle$hypothesis, reference, fluency, adequacy$\rangle$.  In these
experiments, we extend this tuple with automatic scores derived from
$\langle$hypothesis, reference$\rangle$ and examine the
correlations\endnote{The independence of each of these segments is
  questionable, since the same hypothesis translations are used in
  multiple items, but for the sake of methodological comparison with
  prior work, this strategy is preserved.}  between those automatic
scores and the arithmetic mean of the fluency and adequacy measures.

@@

\theendnotes
